A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-10 MSRChallenge2016.tex
some shortening through page 2

\maketitle
\begin{abstract}
  Many implementations of research techniques that automatically repair software
  bugs target programs written in C. Work that targets Java often begins from or
  compares to, direct translations of such techniques to a Java context.  
  However, Java and C are very different languages, and Java should be
  studied to inform the translation of existing approaches to target it.
  We conduct a large-scale study of bug-fixing commits
  to Java projects, focusing on assumptions underlying common
  search-based repair approaches.  We make observations that can be
  leveraged to guide high quality automatic software repair to target Java specifically,
  including common and uncommon statement replacements as conducted by human
  developers and the applicability of previously-proposed patch construction
  operators in the Java context. 
\end{abstract}

@@

There has been considerable attention paid to automatic
program repair in recent
years~\cite{kim2013,legoues2012,pan2009,
  Mechtaev15,Long2016}.
%
One broad class of techniques in this space take a generate-and-validate
approach: \emph{generating} a large number of candidate patches using a
pre-defined set of mutation operators, and then \emph{validating} correctness with
respect to a set of test cases.  Mutation operators range from simple, coarse
granularity statement-level mutations to human-constructed templates learned
from a large corpus of previous human bug-fixing commits.

@@

\vspace{1ex}
\noindent\textbf{How many files are changed to fix a bug?}
%

We consider a file changed if it is new, modified, or deleted in a commit. In
total, $52,052,571$ files were changed, an average of $11.3$ files per
bug-fixing commit, and the median number is $2$.  Although the median number
conforms to our intuition, the average is surprisingly high: most automatic
program repair techniques assume that bugs are local.  We hypothesize several
explanations: Other software artifacts (e.g.  documentation) may be updated
after bug  fixing, or fixing commits may contain changes unrelated to fixing
the bug (e.g.  refactoring, feature addition).  To better understand this
phenomenon, we ask:

\begin{table}
\centering
  \begin{tabular}{ l | r  r }
  \toprule
  File Kind & Total & Average \\ 
  \midrule
  Binary & 752,945 & 0.16 \\ 
  Java (ERROR) & 2,073,558 & 0.45 \\ 
  Java (JLS2) & 2,607,413 & 0.57 \\ 
  Java (JLS3) & 15,748,967 & 3.43 \\
  Java (JLS4)  & 83,798 & 0.02 \\ 
  Text & 541,023 & 0.12 \\ 
  XML & 6,818,299 & 1.49 \\ 
  UNKNOWN & 23,426,568 & 5.10 \\ 
\bottomrule
  \end{tabular}
  \caption{File Types of Changed Files}
  \label{tbl:fileType}
\end{table}
\vspace{1ex}
\noindent\textbf{What are the types of those changed files?}
%
To answer this question, we iterate over all changed files in each bug fixing
revision and count the total number for each file type. Results are shown in
Table~\ref{tbl:fileType}.
%

JAVA (ERROR) files are those that Boa failed to parse. JLS2, JLS3, and JLS4
represent Java files written in different J2SE versions.  We see that text and
binary files are changed least frequently. This is unsurprising, since text
files are often documentation, and binaries should be changed rarely. If we
consider all 4 kinds of Java files as one kind, on average, each bug fixing
revision changes $4.47$ Java files. This does not conform to our assumption of
bug locality. XML files in Java projects usually represent build files;
changing build files is unsurprising.  Rather more surprising is how frequently
UNKNOWN files are changed. Given that all projects are Java projects, it is
unclear whether these are written in other programming languages. We
hypothesize they might be test resources.  To better understand what changes
are usually made to Java files, we next ask:

\vspace{1ex}
\noindent\textbf{How often do developers introduce new classes, methods, fields,
	local variables in
bug fixing commits?} 
%
This question is interesting because most automatic program repair approaches
do not create methods or variable declarations, nor do most explicitly consider
object-oriented features, like fields or classes.

Table~\ref{tbl:new} shows that introducing new
classes and new variables is rare. On average, we still have $0.69$ new methods
per bug fix. These methods naturally contain new test methods (annotated by
@Test, for example), which is not too alarming. However,
what surprises us is that $1.32$ fields are created per bug fix.  This indicates
that automatic program repair approaches should pay attention to the state of
the class when fixing Java programs.

\begin{table}
\centering
  \begin{tabular}{l | r  r }
  \toprule
  Introducing & Total Number & Average \\ \midrule
  Class & 729,201 & 0.16 \\ 
  Methods & 3,186,867 & 0.69 \\ 
  Fields & 6,076,646 & 1.32 \\ 
  Variables & 924,259 & 0.2 \\ 
\bottomrule
  \end{tabular}
  \caption{Introducing new classes, methods, fields, local variables to fix bugs}
  \label{tbl:new}
\vspace{-0.5cm}
\end{table}

@@

Boa's capabilities are powerful, but limited in the precision it enables in
our detection of PAR bug-fixing patterns. For example, it cannot directly \texttt{diff}
two files versions. Thus, rather than finding the exact count of
bug fixing patterns, we approximate by processing pre- and
post-fix files separately.  Additionally, there are
two of the 10 patterns that cannot be easily detected by
Boa, as we describe below. 
%
The patterns we search for are as follows, including our mechanism for
detecting them:

>>>>

\maketitle
\begin{abstract}
  Many implementations of research techniques that automatically repair software
  bugs target programs written in C. Work that targets Java often begins from or
  compares to direct translations of such techniques to a Java context.  
  However, Java and C are very different languages, and Java should be
  studied to inform the construction of repair approaches to target it.
  We conduct a large-scale study of bug-fixing commits
  in Java projects, focusing on assumptions underlying common
  search-based repair approaches.  We make observations that can be
  leveraged to guide high quality automatic software repair to target Java specifically,
  including common and uncommon statement modifications in human patches and the
  applicability of previously-proposed patch construction 
  operators in the Java context. 
\end{abstract}

@@

There has been considerable attention paid to automatic
program repair in recent
years (e.g.,~\cite{kim2013,legoues2012,
  Mechtaev15,Long2016}).
%
One broad class of techniques in this space take a generate-and-validate
approach: \emph{generating} a large number of candidate patches using a
pre-defined set of mutation operators, and then \emph{validating} correctness with
respect to a set of test cases.  Mutation operators range from simple, coarse
granularity statement-level mutations to human-constructed templates learned
from a large corpus of previous human bug-fixing commits.

@@

\vspace{1ex}
\noindent\textbf{How many files are changed to fix a bug?}
%
Most
program repair techniques assume that bugs are local to only one or two files.
We consider a file \emph{changed} if it is new, modified, or deleted in a commit. In
total, $52,052,571$ files were changed, an average of $11.3$ files per
bug-fixing commit. The median number of file changed is $2$.  Although the median
conforms to our intuition, the average is surprisingly high, suggesting a long
tailed distribution.   We hypothesize that
other software artifacts (e.g.  documentation) may be updated
after bug  fixing, or fixing commits may contain changes unrelated to fixing
the bug (e.g.  refactoring, feature addition).  To better understand this
phenomenon, we ask:

\begin{table}
\centering
  \begin{tabular}{ l | r  r }
  \toprule
  File Kind & Total & Average \\ 
  \midrule
  Binary & 752,945 & 0.16 \\ 
  Java (ERROR) & 2,073,558 & 0.45 \\ 
  Java (JLS2) & 2,607,413 & 0.57 \\ 
  Java (JLS3) & 15,748,967 & 3.43 \\
  Java (JLS4)  & 83,798 & 0.02 \\ 
  Text & 541,023 & 0.12 \\ 
  XML & 6,818,299 & 1.49 \\ 
  UNKNOWN & 23,426,568 & 5.10 \\ 
\bottomrule
  \toprule
  Introducing & Total Number & Average \\ \midrule
  Class & 729,201 & 0.16 \\ 
  Methods & 3,186,867 & 0.69 \\ 
  Fields & 6,076,646 & 1.32 \\ 
  Variables & 924,259 & 0.2 \\ 
\bottomrule
  \end{tabular}
  \caption{Top: File Types of Changed Files.  Bottom: Introduction of new
    classes, methods, fields, local variables to fix bugs.   \label{tbl:fileType}\label{tbl:new}}
\vspace{-0.5cm}
\end{table}
\vspace{1ex}
\noindent\textbf{What are the types of those changed files?}
%
The top of Table~\ref{tbl:fileType} shows the types of the changed files in the
Boa dataset. 
Text and
binary files are changed least frequently. This is unsurprising, since such
files are often documentation, and binaries should be changed rarely. 
%
XML files in Java projects usually represent build files;
changing build files is unsurprising.  Rather more surprising is how frequently
UNKNOWN files are changed. Given that all projects are Java projects, it is
unclear whether these are written in other programming languages. We
hypothesize they might be test resources.  JAVA (ERROR) files are those that Boa failed to parse. JLS2, JLS3, and JLS4 are
Java files in different J2SE versions.  If we group
all Java types, on average, each bug fixing
revision changes $4.47$ Java files. This does not conform to our assumption of
bug locality.  To better understand what changes
are usually made to those Java files, we next ask:

\vspace{1ex}
\noindent\textbf{How often do developers introduce new classes, methods, fields,
	local variables in
bug fixing commits?} 
%
This question is interesting because most automatic program repair approaches
do not create methods or variable declarations, nor do most explicitly consider
object-oriented features, like fields or classes. 
%
Table~\ref{tbl:new} shows that introducing new
classes or variables is rare. On average, we still have $0.69$ new methods
per bug fix. These methods include new test methods (annotated by
@Test, for example), which is not too alarming. However, we note
that $1.32$ fields are created per bug fix, suggesting
that automatic program repair approaches should pay attention to the state of
the class when fixing Java programs.

@@

Boa's capabilities are powerful, but limited in the precision it enables in
detection of PAR bug-fixing patterns. For example, it cannot directly \texttt{diff}
two files. Rather than finding exact counts of
bug fixing patterns, we approximate by processing pre- and
post-fix files separately.  Additionally, 
two of the 10 patterns cannot be easily detected by
Boa, as we describe below. 
%
We search for the following patterns:
